### 2016-12-02 Objects/Objects.tex
Adding a little bit about PF

\section{Particle Flow}
\label{sec:objects_pf}

>>>>

\section{\acl{PF}}
\label{sec:objects_pf}
All stable particles are reconstructed and identified using the \ac{PF} algorithm, which
combines the information from all of the different subdetectors of \ac{CMS}. This makes
the identification of particles, and determination of position and momentum, as precise
as possible. All of these particles are then used to build for example jets, \MET and hadronically
decaying taus.
